### 2013-06-24 trunk/network-science/paper.tex

\begin{abstract}
This paper addresses the dynamic properties of typical social networks. We
suppose the evolution over time only includes creating new edges but no
deletion. The paper studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definition is given for our metrics and
also their mathematical analysis. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results could imply
that dynamic centrality is more capable in spotting hot social events.

@@

\section{Introduction}
Social networks is a surprising interdisciplinary field of social science and
computer science, allowing helpful analysis of large-scaled social behavior
and tendency. In this paper, we will deal with more information of social
networks, the time dimension, and make a similar study to the social behaviors.
We build metrics for evolving social networks and design an algorithm to
calculate them. We compare how different the outcome by our method would be
against the classical analysis with un-timestamped data mining.

>>>>

\begin{abstract}
This article addresses the dynamic properties of typical social networks. By
supposing that the evolution over time only includes creating new edges but no
deletion, we studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definitions are given to our metrics and
their mathematical analysis are put. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results could imply
that dynamic centrality is more capable in spotting hot social events.

@@

\section{Introduction}
Social networks is a surprising interdisciplinary field of social science and
computer science, allowing helpful analysis of large-scaled social behavior
and tendency. In this article, we are able to deal with more information, the
time dimension, of social networks, and make a similar study to the social
behaviors.  We build metrics for evolving social networks and design an
algorithm to calculate them. We compare out results with the classical analysis
which works under un-timestamped data.
